Dependent Object Types

### 2012-09-07 doc/candidacy/slides.tex
ex of limitation, with caveat

\begin{frame}{SML modules}
\begin{description}[type-sharing]
\item[structure] a module\\a collection of types, values and
  (sub)structures packaged as a program unit.
\item[signature] an interface; the type of a structure\\description of
  the types, values and (sub)structures of a structure given by their
  kinds, types and interfaces.
\item[functor] a function mapping structures to structures
\item[type-sharing] enables stating that types specified in separate
  modules are actually equal
\end{description}
% example?
\end{frame}

@@

\begin{frame}{Limitations of SML modules}
\begin{itemize}
\item modules are not first-class; e.g. not possible to return a
  structure from an {\tt if} expression
\item type sharing is restricted to equality between type names, not
  general type expressions; in effect, transparency / opaqueness of a
  signature cannot be fully fined-tuned % example?
\end{itemize}
\end{frame}

>>>>

\begin{frame}{SML modules}
\begin{description}[type-sharing]
\item[structure] a module\\a collection of types, values and
  (sub)structures packaged as a program unit.
\item[signature] an interface; the type of a structure\\description of
  the types, values and (sub)structures of a structure given by their
  kinds, types and interfaces.
\item[functor] a function mapping structures to structures
\item[type-sharing] enables stating that types specified in separate
  modules are actually equal
\end{description}
\end{frame}

@@

\begin{frame}[fragile]{Limitations of SML modules}
\begin{itemize}
\item modules are not first-class; e.g. not possible to return a
  structure from an {\tt if} expression
\item type sharing is restricted to equality between type names, not
  general type expressions (limitation of SML '90; lifted in SML '97)
\begin{minted}{sml}
signature X' = sig
  type T
  type T2T = T -> T
  val v: T
  val f: T2T
end
\end{minted}
\item in effect, transparency / opaqueness of a signature cannot be
  fully fined-tuned
\end{itemize}
\end{frame}
